Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-06 sattose/paper.tex
Working on the table

\section{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. To be able to refactor detected clones, it is useful to have the ability to rewrite the AST. We considered a set of clone detection tools for their ability to support the refactoring process automatically. \todo{didn't you have to build a matrix with features etc? where is it? this would be the place for it} None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.

@@

The results of our survey is displayed in table \ref{table:dettools}.

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \bigskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool}                                                                                                                           & \textbf{Short Description}                                                          & \textbf{(1)}                  & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese}                                                                                                              & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ large scale clone\\ detection\end{tabular} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}      & \begin{tabular}[c]{@{}l@{}}Duplicated code\\ refactoring advisor\end{tabular}       & ?                             & ?            & ✗            & ✓            \\ \hline
CPD \cite{roy2009comparison}\footnote{CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.} & \begin{tabular}[c]{@{}l@{}}Widely used clone\\ detection tool\end{tabular}          & ✓                             & ✓            & ✗            & ✗            \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Widely used\\ clone detection\\ framework\end{tabular}   & ✓                             & ✓            & ✗            & ✗            \\ \hline
CCFinderSW \cite{semura2017ccfindersw}                                                                                                                 & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ clone detection\end{tabular}               & ✓                             & ✗            & ✗            & ✓            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular}                                         & \begin{tabular}[c]{@{}l@{}}These tools detect\\ all types of clones\end{tabular}    & ✓                             & ✗            & ✗            & ✓            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}                                                                                                          & \begin{tabular}[c]{@{}l@{}}Large-scale clone\\ detection\end{tabular}               & ✓                             & ✓            & ✗            & ✗            \\ \hline
Deckard \cite{jiang2007deckard}                                                                                                                        & \begin{tabular}[c]{@{}l@{}}ANTRL Parse Tree\\ based Clone Detector\end{tabular}     & ✓                             & ✗            & ✓            & ✗            \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

>>>>

\section{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.

@@

The results of our survey are displayed in table \ref{table:dettools}.

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \bigskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{}           & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison}\footnote{} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
\end{tabular}
\end{center}
\end{table}

None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.

\footnotetext[3]{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}

\footnotetext{\label{note1}CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.}

@@

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}
